Figures and Tables

### 2021-02-02 paper/figures_tables.Rmd
supp updates

```{r libraries}
library(ggplot2)
library(aracari)
library(cowplot)
library(dplyr)
library(extRemes)

@@

@@

## Seed dispersal distances and aggregation
#### Figure 4. Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates. **A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates. Each individual line represents the dispersal kernel generated by each individual animal. The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group. **B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models. **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models. *Is there more comparison I should mention here? Like, how the larger values are more abundant in the individual model?*

@@

The mean dispersal in the boxplots is not the same as the dispersal distances before. This mean dispersal is the distance from the origin to the mean seed location in each simulation run. The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1.

```{r}
knitr::kable(dispersal_kernel_table %>% 
               rename(Long_distance = LDD))
```

@@

>>>>

```{r libraries}
library(ggplot2)
library(aracari)
library(cowplot)
library(dplyr)
library(extRemes)
library(moments)
library(fitdistrplus)

@@

## Methods

@@

## Seed dispersal distances and aggregation
#### Figure 4. Seed dispersal distances and aggregation metrics for simulated seeds in the three models considering variation in animal movement rates. **A.** Density kernels for frugivore-generated seed dispersal distances for each seed simulated under the three models of variation in animal movement rates. Each individual line represents the dispersal kernel generated by each individual animal. The null model assumes the same movement rate for all animals, whereas individual and family models use a movement rate for each animal id, or family group. **B.** Box plot comparing the distances from the parent tree at the origin to the mean seed location in each simulation run among the three simulation models. **C.** Box plot comparing the seed aggregation metric, seed dispersion, for each simulation run between the three simulation models. The mean seed location is used to calculate dispersion, as the average distance of each seed to the mean seed location, as shown in Figure 1. *Is there more comparison I should mention here? Like, how the larger values are more abundant in the individual model?*

@@

#### Table 1. Summary table of seed dispersal metrics for each of the simulation models. Seed dispersal and seed dispersion metrics represent the average value for each of the models, with standard errors in parentheses. Kurtosis is calculated for each of the three simulation models as described in the main text. Maximum seed dispersal distance represents the longest dispersal distance out of all seeds dispersed for each of the simulation models. Long-distance dispersal events are calculated as the percentage of seed dispersal distances greater than 500m for each simulated individual, with standard deviations calculated between the individuals in each simulation model.

```{r}
knitr::kable(dispersal_kernel_table)
```

@@

## Supplementary Figures and tables

### Threshold diagnostic plots
```{r}
aligned_plots(null_mrl, null_threshplot, orig_thres, title = "Null model")
aligned_plots(indiv_mrl, indiv_threshplot, orig_thres, title = "Individual model")
aligned_plots(fam_mrl, fam_threshplot, orig_thres, title = "Family model")
```
